Causal Distillation Trees

### 2025-02-12 causalDT-manuscript/notebooks/paper_figures.Rmd
clean up figures

KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Distilled Rlasso",
  "Virtual Twins",
  "Causal Tree (pruned)",
  "Causal Tree (unpruned)",
  "Linear Regression",
  "Lasso"
)
COLORS <- c(
  # "Distilled Causal Forest" = "#3153A5",
  "Distilled Causal Forest" = "#1f5d8f",
  # "Distilled Causal Forest" = "#5d8cae",
  # "Distilled Rboost" = "#94B1c9",
  # "Distilled Rboost" = "#678096",
  ## "Distilled Rboost" = "#79b2dd",
  "Distilled Rboost" = "#6aafe4",
  # "Distilled Rboost" = "#6DA7D3",
  # "Distilled Rboost" = "#6DA7D3",
  # "Distilled Rlasso" = "#ACC2D0",
  "Distilled Rlasso" = "#9ab6c8",
  # "Distilled Rlasso" = "#B8CEDD",
  "Virtual Twins" = "#768c50",
  # "Virtual Twins" = "#6F9940",
  "Causal Tree (pruned)" = "#953a2f",
  "Causal Tree (unpruned)" = "#DB9685",
  # "Linear Regression" = "#DAA520",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
  # "Lasso" = "#e4d2a4"
)

FACET_LABS <- list(
  "0.2" = "Weak",
  "0.6" = "Moderate",
  "1" = "High"
)
signal_labeller <- function(variable, value) {
  if (variable == "tau_heritability") {
    return(FACET_LABS[as.character(value)])
  } else {
    return(value)
  }
}

@@

```{r}
EXP_NAME <- "Test"
source(here::here(file.path("meals", "setup.R")))
source(here::here(file.path("meals", "shared_dgps.R")))
source(here::here(file.path("meals", "shared_methods.R")))
source(here::here(file.path("meals", "shared_evaluators.R")))
source(here::here(file.path("meals", "shared_visualizers.R")))
source(here::here(file.path("meals", "shared_experiments.R")))
experiment <- experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )
```

```{r results = "asis"}
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND with Linear Covariates DGP",
  "Additive with Linear Covariates DGP",
  "OR with Linear Covariates DGP"
)
sim_results_dir <- here::here(
  file.path("results", "Unbiased W")
)

plt_subgroup_ls <- list()
plt_subgroup2_ls <- list()
plt_thresholds_ls <- list()
plt_stability_ls <- list()
plt_freq_ls <- list()
for (sim_name in sim_names) {
  cat(sprintf("\n\n## %s {.tabset .tabset-pills .tabset-square}\n\n", sim_name))

  # fit_results <- readRDS(
  #   file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
  # ) |>
  #   dplyr::filter(
  #     .method_name %in% !!KEEP_METHODS
  #   )
  # eval_results <- evaluate_experiment(experiment, fit_results)
  # viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  # 
  # plt_selection <- viz_results$`Subgroup Feature Selection Errors Plot` +
  #   ggplot2::scale_color_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::scale_fill_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   )
  # 
  # plt_cate <- viz_results$`Subgroup CATE Errors Plot` +
  #   ggplot2::scale_color_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::scale_fill_manual(
  #     breaks = KEEP_METHODS,
  #     values = COLORS
  #   ) +
  #   ggplot2::labs(
  #     y = "CATE RMSE"
  #   ) +
  #   vthemes::theme_vmodern(
  #     axis_title_size = 16,
  #     axis_text_size = 12,
  #     legend_title_size = 16,
  #     legend_text_size = 12
  #   ) +
  #   ggplot2::theme(
  #     strip.background = ggplot2::element_blank(),
  #     strip.placement = "outside"
  #     # strip.background = ggplot2::element_rect(
  #     #   color = "transparent", fill = "transparent"
  #     # ),
  #     # strip.text = ggplot2::element_text(
  #     #   color = "black", face = "bold", size = 16
  #     # )
  #   ) +
  #   ggplot2::guides(
  #     color = "none", fill = "none"
  #   )
  # 
  # pplt <- patchwork::wrap_plots(
  #   plt_selection, plt_cate, nrow = 1, guides = "collect",
  #   widths = c(3.5, 1)
  # ) &
  #   ggplot2::labs(x = NULL)
  # plt_subgroup_ls[[sim_name]] <- pplt
  # plt <- patchwork::wrap_elements(pplt) +
  #   ggplot2::labs(
  #     tag = expression(
  #       bold(paste("Proportion of Variance Explained in ", tau))
  #     )
  #   ) +
  #   ggplot2::theme(
  #     plot.tag = ggplot2::element_text(
  #       size = 16
  #     ),
  #     plot.tag.position = c(0.45, 0),
  #     plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  #   )
  # plt_subgroup2_ls[[sim_name]] <- plt

  fit_results <- readRDS(
    file.path(sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds")
  ) |>
    dplyr::filter(
      .method_name %in% !!KEEP_METHODS,
      tau_heritability %in% c(0.2, 0.6, 1)
    )
  eval_results <- evaluate_experiment(experiment, fit_results)
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)

  plt_thresholds <- viz_results$`Subgroup Thresholds Distribution Plot` +
    ggplot2::scale_color_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::scale_fill_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::facet_grid(.var ~ tau_heritability, labeller = signal_labeller)
  plt_thresholds_ls[[sim_name]] <- plt_thresholds

  plt_stability <- viz_results$`Subgroup Stability Diagnostics Plot`[[1]] +
    ggplot2::scale_color_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::scale_fill_manual(
      breaks = KEEP_METHODS,
      values = COLORS,
      labels = stringr::str_remove(KEEP_METHODS, " \\(pruned\\)")
    ) +
    ggplot2::facet_grid(~ tau_heritability, labeller = signal_labeller) +
    ggplot2::coord_cartesian(xlim = c(1, 4)) +
    ggplot2::scale_x_continuous(
      breaks = 1:4
    ) +
    ggplot2::labs(
      x = "Tree Depth",
      y = "Mean Jaccard Stability",
      color = "Method",
      fill = "Method"
    ) +
    vthemes::theme_vmodern(size_preset = "medium")
  plt_stability_ls[[sim_name]] <- plt_stability

  plt_nsplits <- viz_results$`Number of Splits Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.05, end = 1, option = "magma", limits = c(0., 7)
    )
  plt_ntrees <- viz_results$`Number of Trees Plot` +
    ggplot2::facet_grid(tau_heritability ~ ., labeller = signal_labeller) +
    viridis::scale_fill_viridis(
      begin = 0.05, end = 1, option = "magma", limits = c(0, 100)
    )
  plt <- patchwork::wrap_plots(
    plt_ntrees, plt_nsplits, nrow = 1
  ) +
    patchwork::plot_layout(
      axis_titles = "collect_y"
    ) &
    ggplot2::labs(
      x = "Variable"
    )

  plt_freq_ls[[sim_name]] <- plt
}
```

```{r}
plt_subgroup <- purrr::map2(
  plt_subgroup_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_subgroup_ls[idx])
    tag <- LETTERS[idx]
    if (sim_name != names(plt_subgroup_ls[2])) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
      hjust <- 0.78
    } else {
      hjust <- 0.82
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, 0.48),
        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
      # ggplot2::theme(
      #   plot.title = ggplot2::element_text(
      #     size = 16, face = "bold", hjust = hjust
      #   ),
      #   plot.title.position = "plot"
      # )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  ) |>
  patchwork::wrap_elements() +
  ggplot2::labs(
    tag = expression(
      bold(paste("Proportion of Variance Explained in ", tau))
    )
  ) +
  ggplot2::theme(
    plot.tag = ggplot2::element_text(
      size = 16
    ),
    plot.tag.position = c(0.45, 0),
    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  )
ggplot2::ggsave(
  plt_subgroup, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9, 
  width = 14
)

plt_subgroup_cov <- purrr::map2(
  plt_subgroup_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name_orig <- names(plt_subgroup_ls[idx])
    sim_name <- stringr::str_replace(
      sim_name_orig, "with", "DGP with\n"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    if (sim_name_orig != names(plt_subgroup_ls[5])) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
      hjust <- 0.78
    } else {
      hjust <- 0.82
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.06, 0.48),
        plot.margin = ggplot2::unit(c(-0.1, 0, 0, 0.75), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
      # ggplot2::theme(
      #   plot.title = ggplot2::element_text(
      #     size = 16, face = "bold", hjust = hjust
      #   ),
      #   plot.title.position = "plot"
      # )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  ) |>
  patchwork::wrap_elements() +
  ggplot2::labs(
    tag = expression(
      bold(paste("Proportion of Variance Explained in ", tau))
    )
  ) +
  ggplot2::theme(
    plot.tag = ggplot2::element_text(
      size = 16
    ),
    plot.tag.position = c(0.45, 0),
    plot.margin = ggplot2::unit(c(-0.1, 0, .2, -0.1), units = "in")
  )
ggplot2::ggsave(
  plt_subgroup_cov, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9, 
  width = 14
)
```

```{r}
plt_thresholds <- purrr::map2(
  plt_thresholds_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_thresholds_ls[idx])
    tag <- LETTERS[idx]
    plt <- plt +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1, guides = "collect"
  ) +
  patchwork::plot_layout(
    axes = "collect"
  )
ggplot2::ggsave(
  plt_thresholds, 
  filename = file.path(FIG_DIR, "sim_thresholds.pdf"),
  height = 10, 
  width = 11
)

plt_thresholds_cov <- purrr::map2(
  plt_thresholds_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name <- stringr::str_replace(
      names(plt_thresholds_ls[idx]), "with", "DGP with\n"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    plt <- plt +
      ggplot2::labs(
        title = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        panel.background = ggplot2::element_rect(
          fill = "grey98"
        ),
        panel.grid.major = ggplot2::element_line(
          color = "grey98"
        )
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1, guides = "collect"
  ) +
  patchwork::plot_layout(
    axes = "collect"
  )
ggplot2::ggsave(
  plt_thresholds_cov, 
  filename = file.path(FIG_DIR, "sim_thresholds_cov.pdf"),
  height = 10, 
  width = 11
)
```

```{r}
# plt_ntrees_ls <- purrr::map(
#   plt_freq_ls[1:3], ~ .x[[1]]
# )
# plt_nsplits_ls <- purrr::map(
#   plt_freq_ls[1:3], ~ .x[[2]]
# )
# plt_ntrees <- patchwork::wrap_plots(
#   plt_ntrees_ls, nrow = 1, guides = "collect"
# ) +
#   patchwork::plot_layout(
#     axes = "collect"
#   )

plt_freq <- purrr::map2(
  plt_freq_ls[1:3], 1:3,
  function(plt, idx) {
    sim_name <- names(plt_freq_ls[idx])
    tag <- LETTERS[idx]
    plt <- patchwork::wrap_elements(plt) +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        plot.tag.position = c(0.47, 1.02),
        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt_freq, 
  filename = file.path(FIG_DIR, "sim_freq.pdf"),
  height = 16, 
  width = 14
)

plt_freq_cov <- purrr::map2(
  plt_freq_ls[4:6], 4:6,
  function(plt, idx) {
    sim_name <- stringr::str_replace(
      names(plt_freq_ls[idx]), "with", "DGP with"
    ) |>
      stringr::str_remove(" DGP$")
    tag <- LETTERS[idx - 3]
    plt <- patchwork::wrap_elements(plt) +
      ggplot2::labs(
        tag = sprintf("(%s) %s", tag, sim_name)
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5
        ),
        plot.tag.position = c(0.47, 1.02),
        plot.margin = ggplot2::unit(c(0.3, 0, 0, 0.5), units = "in")
      )
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt_freq_cov, 
  filename = file.path(FIG_DIR, "sim_freq_cov.pdf"),
  height = 16, 
  width = 14
)
```

>>>>

COLORS <- c(
  "Distilled Causal Forest" = "#1f5d8f",
  "Distilled Rboost" = "#6aafe4",
  "Virtual Twins" = "#768c50",
  "Causal Tree" = "#953a2f",
  "Linear Regression" = "#b2954a",
  "Lasso" = "#D2BE90"
)
CROSSFIT_COLORS <- c(
  "#981643", "#ED724F", "#F8B06E", "#FCE096", "#8FB989", "#4287B7", "#5E519B"
)
RULEFIT_COLORS <- c(
  "CART" = "#1f5d8f",
  "Rulefit (linear + rules, max depth = 3)" = "#FF9300",
  "Rulefit (linear + rules, max depth = 2)" = "#E7298A",
  "Rulefit (rules only, max depth = 3)" = "#66A61E",
  "Rulefit (rules only, max depth = 2)" = "#7570B3"
)
LINE_TYPES <- c(
  "Pruned" = "solid",
  "Unpruned" = "dashed"
)

FACET_LABS <- list(
  "0.2" = "Weak (0.2)",
  "0.6" = "Moderate (0.6)",
  "1" = "Strong (1)"
)
signal_labeller <- function(variable, value) {
  if (variable == "tau_heritability") {
    return(FACET_LABS[as.character(value)])
  } else if (variable == "metric") {
    return(METRIC_LABS[as.character(value)])
  } else {
    return(value)
  }
}

add_pruned_column <- function(data) {
  data |> 
    dplyr::mutate(
      .is_pruned = dplyr::case_when(
        stringr::str_detect(.method_name, "unpruned") ~ "Unpruned",
        TRUE ~ "Pruned"
      ),
      .method_name = stringr::str_remove(.method_name, " \\(unpruned\\)")
    )
}

@@

```{r}
EXP_NAME <- "Test"
source(here::here(file.path("meals", "setup.R")))
source(here::here(file.path("meals", "shared_dgps.R")))
source(here::here(file.path("meals", "shared_methods.R")))
source(here::here(file.path("meals", "shared_evaluators.R")))
source(here::here(file.path("meals", "shared_visualizers.R")))
source(here::here(file.path("meals", "shared_experiments.R")))
experiment <- experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )

example_experiment <- example_experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    n = c(100, 500, 1000, 2000)
  )

crossfit_experiment <- crossfit_experiment |>
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )

rulefit_experiment <- rulefit_experiment |> 
  add_dgp(gaussian_X_unbiased_Z_and) |>
  add_vary_across(
    .dgp = gaussian_X_unbiased_Z_and$name,
    tau_heritability = c(0.2, 0.4, 0.6, 0.8, 1)
  )
```

## Example {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- here::here(
  file.path("results", "Main Simulations")
)
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND with Linear Covariates DGP",
  "Additive with Linear Covariates DGP",
  "OR with Linear Covariates DGP"
)

keep_methods_ls <- list(
  "causal_tree_only" = c("Causal Tree"),
  "all_methods" = c("Distilled Causal Forest", "Causal Tree")
)

for (keep_methods_idx in 1:length(keep_methods_ls)) {
  keep_methods <- keep_methods_ls[[keep_methods_idx]]
  keep_methods_name <- names(keep_methods_ls)[keep_methods_idx]
  for (sim_name in sim_names) {
    fit_results <- readRDS(
      file.path(
        sim_results_dir, sim_name, "Varying n", "fit_results.rds"
      )
    )
    eval_results <- readRDS(
      file.path(
        sim_results_dir, sim_name, "Varying n", "eval_results.rds"
      )
    )
    viz_results <- visualize_experiment(
      example_experiment, fit_results, eval_results
    )

    plt <- viz_results$`Number of Subgroups Plot`
    plt$data <- plt$data |> 
      dplyr::filter(
        .method_name %in% !!keep_methods
      )
    plt <- plt +
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98")
      )
    ggplot2::ggsave(
      plt, 
      filename = file.path(
        FIG_DIR, 
        sprintf("sim_example_nsubgroup_%s.pdf", keep_methods_name)
      ),
      height = 3.1,
      width = 11.5
    )
  }
}
```

## Main Simulations {.tabset .tabset-pills .tabset-pills-square}

```{r results = "asis"}
sim_results_dir <- here::here(
  file.path("results", "Main Simulations")
)
SIM_NAMES <- c(
  "AND DGP" = "AND DGP",
  "Additive DGP" = "Additive DGP",
  "OR DGP" = "OR DGP",
  "AND with Linear Covariates DGP" = "AND DGP with Linear Covariates",
  "Additive with Linear Covariates DGP" = "Additive DGP with Linear Covariates",
  "OR with Linear Covariates DGP" = "OR DGP with Linear Covariates"
)

# load in results
eval_results_ls <- list()
viz_results_ls <- list()
for (sim_name in names(SIM_NAMES)) {
  fit_results <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying tau_heritability", "fit_results.rds"
    )
  )
  eval_results <- readRDS(
    file.path(
      sim_results_dir, sim_name, "Varying tau_heritability", "eval_results.rds"
    )
  )
  viz_results <- visualize_experiment(experiment, fit_results, eval_results)
  eval_results_ls[[SIM_NAMES[[sim_name]]]] <- eval_results
  viz_results_ls[[SIM_NAMES[[sim_name]]]] <- viz_results
}
```

### Selected Subgroup Features + Threshold Distances + Estimated Subgroup ATEs

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Rboost",
  "Virtual Twins",
  "Causal Tree",
  "Linear Regression",
  "Lasso"
)

## without covariates
sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt

    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )

    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")

    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2

    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(legend.position = "bottom")

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.03, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors.pdf"),
  height = 9.5, 
  width = 15
)

## with covariates
sim_names <- c(
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_selection <- plt

    plt <- viz_results_ls[[sim_name]]$`Subgroup ATE Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      )
    plt_cate <- plt +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12),
        legend.title = ggplot2::element_text(face = "bold", size = 16),
        legend.text = ggplot2::element_text(size = 12)
      )

    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X1"
      )
    plt_thr1 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(1), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")

    plt <- viz_results_ls[[sim_name]]$`Threshold Distances Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS,
        .var == "X2"
      )
    plt_thr2 <- plt +
      ggplot2::labs(
        y = expression(
          bold(paste(X^(2), " Threshold RMSE"))
        )
      ) +
      ggplot2::theme(
        strip.background = ggplot2::element_blank(),
        strip.text = ggplot2::element_blank(),
        strip.placement = "outside",
        axis.title.y = ggplot2::element_text(face = "bold", size = 16),
        axis.text = ggplot2::element_text(size = 12)
      ) +
      ggplot2::guides(color = "none", fill = "none", linetype = "none")
    plt_thr <- plt_thr1 + plt_thr2

    plt <- patchwork::wrap_plots(
      plt_selection, plt_thr, plt_cate, nrow = 1, guides = "collect",
      widths = c(3.5, 2.35, 1)
    ) &
      ggplot2::labs(x = NULL) &
      ggplot2::theme(legend.position = "bottom")

    if (sim_name != sim_names[3]) {
      plt <- plt &
        ggplot2::guides(
          color = "none", fill = "none"
        )
    }
    tag_pos <- dplyr::case_when(
      sim_name == sim_names[1] ~ 0.45,
      sim_name == sim_names[2] ~ 0.53,
      sim_name == sim_names[3] ~ 0.66
    )
    if (sim_name == sim_names[1]) {
      plt[[1]] <- plt[[1]] +
        ggplot2::labs(
          title = "(A) Subgroup Features"
        )
      plt[[2]] <- plt[[2]] +
        ggplot2::labs(
          title = "(B) Subgroup Thresholds"
        )
      plt[[3]] <- plt[[3]] +
        ggplot2::labs(
          title = "(C) Subgroup ATEs"
        )
    }
    plt[[1]] <- plt[[1]] +
      ggplot2::labs(
        tag = plt_name
      ) +
      ggplot2::theme(
        plot.tag = ggplot2::element_text(
          size = 18, face = "italic", angle = 90, hjust = 0.5, vjust = 1
        ),
        plot.tag.position = c(-.08, tag_pos),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0.5), units = "in")
      )
    plt <- plt &
      ggplot2::theme(
        panel.background = ggplot2::element_rect(fill = "grey98"),
        panel.grid.major = ggplot2::element_line(color = "grey98"),
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.5, vjust = -1
        )
      )
    plt[[2]] <- plt[[2]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 1.5, vjust = -1
        ),
        plot.margin = ggplot2::unit(c(0, 0.35, 0, 0), units = "in")
      )
    plt[[3]] <- plt[[3]] +
      ggplot2::theme(
        plot.title = ggplot2::element_text(
          size = 18, face = "italic", hjust = 0.75, vjust = -1
        )
      )
    if (sim_name == sim_names[3]) {
      plt <- plt +
        ggplot2::labs(
          x = expression(
            bold(paste("Proportion of Variance Explained in ", tau, " by Covariates"))
          )
        ) +
        ggplot2::theme(
          axis.title.x = ggplot2::element_text(face = "bold", size = 16, hjust = 2.1, vjust = -1.25)
        )
    }
    return(plt)
  }
) |>
  patchwork::wrap_plots(
    ncol = 1
  )
ggplot2::ggsave(
  plt, 
  filename = file.path(FIG_DIR, "sim_subgroup_errors_cov.pdf"),
  height = 9.5, 
  width = 15
)
```

```{r}
KEEP_METHODS <- c(
  "Distilled Causal Forest",
  "Distilled Causal Forest (unpruned)",
  "Distilled Rboost",
  "Distilled Rboost (unpruned)",
  "Causal Tree",
  "Causal Tree (unpruned)"
)

sim_names <- c(
  "AND DGP",
  "Additive DGP",
  "OR DGP",
  "AND DGP with Linear Covariates",
  "Additive DGP with Linear Covariates",
  "OR DGP with Linear Covariates"
)
plt <- purrr::map(
  sim_names,
  function(sim_name) {
    plt_name <- stringr::str_replace(sim_name, "with ", "with\n")
    plt <- viz_results_ls[[sim_name]]$`Subgroup Feature Selection Errors Plot`
    plt$data <- plt$data |>
      dplyr::filter(
        .method_name %in% KEEP_METHODS
      ) |> 
      add_pruned_column()
    plt$layers[[1]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      ymin = mean_feature_selection_err - se_feature_selection_err,
      ymax = mean_feature_selection_err + se_feature_selection_err,
      fill = .method_name,
      group = interaction(.method_name, .is_pruned)
    )
    plt$layers[[2]]$mapping <- ggplot2::aes(
      x = tau_heritability, 
      y = mean_feature_selection_err,
      color = .method_name,
      linetype = .is_pruned, 
      group = interaction(.method_name, .is_pruned)
    )
    plt_selection <- plt +
      ggplot2::scale_linetype_manual(
        values = LINE_TYPES
      )
